### 2015-02-11 paper/paths.tex
fixed a typo

  let y: ~int = *x; // *x is now deinitialized
  // Here the shadow of x is `~ uninit' and the shadow of y is `~ int'
  // x is initialized, by *x and **x are not
  // both y and *y are initialized
}
\end{verbatim}

>>>>

  let y: ~int = *x; // *x is now deinitialized
  // Here the shadow of x is `~ uninit' and the shadow of y is `~ int'
  // x is initialized, but *x and **x are not
  // both y and *y are initialized
}
\end{verbatim}
